Interpreting the gas-fraction as the entropy of an isothermal dusty gas

### 2016-07-29 model.tex
polishing up model section

\subsection{Strictly isothermal gas well-coupled to dust} 
Now consider constant $c_s$ but $\tstop\neq0$. Then Eq. \ref{int_rel}
gives 
\begin{align}
  s = -\frac{\imag\int \left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}dV}{2\omega\int\rho\left(|\dd
    v_r|^2 + |\dd v_z|^2\right)dV}, 
\end{align}
%In this case 
%the effective energy equation is 
%\begin{align}\label{dusty_cooling}
%  \frac{DP}{Dt} &= - P \nabla \cdot \bm{v} + \mathcal{C}
%\end{align} 
%The function $\mathcal{C}$ can be considered as a cooling term. 
%By
%analogy with enabling VSI in an adiabatic gas through cooling
%\citep{nelson13,lin15}, we may expect a `dusty VSI' to develop 
%if this term is large enough (physically meaning diffusion of the
%dust-fraction is strong). 
%Note that $\mathcal{C}$ is also responsible for the streaming
%instability  in the strong-drag limit \citep{laibe14}, though this
%does not require vertical stratification. In the form of
%Eq. \ref{dusty_cooling}, however, the streaming instability has a
%thermodynamical interpretation, similar to thermal instabilities in
%stars \citep{latter06}.  
which represent all instabilities due to large-but-finite dust-gas
friction. The formalism we have adopted give these instabilities a 
thermodynamical interpretation \citep[thermal instabilities in
  stars][]{latter06} because the dust-gas friction enters the problem
as an energy source term. This includes the streaming instability in
the strong-drag limit \citep{youdin05a, jacquet11, laibe14}.

>>>>

\subsection{Strictly isothermal gas well-coupled to dust} 
Now consider constant $c_s$ but $\tstop\neq0$. Then Eq. \ref{int_rel}
gives 
\begin{align}
  s = -\frac{\imag\int \left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}dV}{2\omega\int\rho\left(|\dd
    v_r|^2 + |\dd v_z|^2\right)dV}, 
\end{align}
%In this case 
%the effective energy equation is 
%\begin{align}\label{dusty_cooling}
%  \frac{DP}{Dt} &= - P \nabla \cdot \bm{v} + \mathcal{C}
%\end{align} 
%The function $\mathcal{C}$ can be considered as a cooling term. 
%By
%analogy with enabling VSI in an adiabatic gas through cooling
%\citep{nelson13,lin15}, we may expect a `dusty VSI' to develop 
%if this term is large enough (physically meaning diffusion of the
%dust-fraction is strong). 
%Note that $\mathcal{C}$ is also responsible for the streaming
%instability  in the strong-drag limit \citep{laibe14}, though this
%does not require vertical stratification. In the form of
%Eq. \ref{dusty_cooling}, however, the streaming instability has a
%thermodynamical interpretation, similar to thermal instabilities in
%stars \citep{latter06}.  
which represent all instabilities due to large-but-finite dust-gas
friction. The formalism we have adopted give these instabilities a 
thermodynamical interpretation because the dust-gas friction enters the problem
as an energy source term \citep[cf. thermal instabilities in
  stars][]{latter06}. 
This includes the streaming instability in
the strong-drag limit \citep{youdin05a, jacquet11, laibe14}.
